Data preparation: Study 1_2019

### 2023-05-18 processing/preparation_study1_2019.Rmd
submission IJS

---
title: "Data preparation: Study 1"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "show"
editor_options:
  chunk_output_type: console
---

@@

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```
This is the preparation code of the data for Study 1: Measuring meritocracy with international secondary data. The prepared data is `data_s1.RData`

@@

```{r}
issp2009 <- read_dta("input/data/original/ZA5400_v4-0-0.dta")
```

@@

```{r }
names(issp2009) <- tolower(names(issp2009))
# Check & generate IDs (v4: respondent, v5: country)
tapply(issp2009$v4, issp2009$v5, mean, na.rm = TRUE)
# Algunos paises (ej:826) tienen ids raros ...
# Generar nueva id secuencial individuos por país para merges
issp2009$id <- sequence(tabulate(issp2009$v5))
tapply(issp2009$id, issp2009$v5, mean, na.rm = TRUE) # ok
summary(issp2009$id)
issp2009$idtem = issp2009$v5 * 10000
issp2009$id = issp2009$idtem + issp2009$id
```

@@

*  v6: wealthy family
*  v7: educated parents
*  v9: ambition 
* v10: hard work 
* v11: right people
* v12: political connections
* v14: race 
* v16: gender 
* IDs: v5 (country) & id (individual id)

>>>>

---
title: "Data preparation: Study 1_2019"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "show"
editor_options:
  chunk_output_type: console
---

## Note: this is an update  of the original study_1 (which used 2009 data) Here we use the last available file from wave 2019.

@@

```{css, echo=FALSE}
# /* expandir el espacio del documento*/
body .main-container {
      max-width: 1600px !important;
      width: 1600px !important;
    }
#/* expandir width de la TOC*/
div.tocify {
    width: 22% !important;
    max-width: 331px !important;
    max-height: 102% !important;
}
```
This is the preparation code of the data for Study 1_2019: Measuring meritocracy with international secondary data. The prepared data is `data_s1_2019.RData`

@@

```{r}
issp2019 <- read_dta("input/data/original/ZA7600_v3-0-0.dta")
```

@@

```{r }
names(issp2019) <- tolower(names(issp2019))
find_var(data = issp2019,"country") # country and c_sample
find_var(data = issp2019,"id") #caseid
dplyr::n_distinct(issp2019$caseid) # ok, id única por caso

# Check & generate IDs (caseid: respondent, country: country)
tapply(issp2019$country, issp2019$caseid, mean, na.rm = TRUE)
# Algunos paises (ej:826) tienen ids raros ...
# Generar nueva id secuencial individuos por país para merges
issp2019$id <- sequence(tabulate(issp2019$country))
tapply(issp2019$id, issp2019$country, mean, na.rm = TRUE) # ok
summary(issp2019$id)
issp2019$idtem = issp2019$country * 10000
issp2019$id = issp2019$idtem + issp2019$id
```

@@

*  v1: wealthy family
*  v2: educated parents
*  XX: ambition 
*  v4: hard work 
*  v5: right people
*  v6: political connections
*  v8: race 
* v10: gender 
* IDs: v5 (country) & id (individual id)
